---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/",
  out.width = "100%"
)
```

# myregression

*A lightweight teaching package illustrating least squares estimation via optimization and bootstrap inference.*

---

## Overview

`myregression` provides a simple example of fitting linear models using **numerical optimization (`optim`)** instead of the analytical OLS formula, and demonstrates how to obtain **bootstrap standard errors** and confidence intervals.

The package defines:

- `ls_loss()` — least-squares loss function  
- `my_lm()` — estimator using `optim()` and bootstrap covariance  
- S3 methods: `print()`, `coef()`, `vcov()`, `fitted()`, `residuals()`, `predict()`, `summary()`, `plot_marginals()`

This is ideal for illustrating numerical optimization, resampling, and custom S3 interfaces in R.

---

## Installation

```r
# Install development tools if needed
install.packages("devtools")

# Install from GitHub
devtools::install_github("R-4-Data-Science/myregression")
```

---

## Quick Example

```{r example, message=FALSE}
library(myregression)

set.seed(1)
n <- 100; p <- 3
X <- matrix(rnorm(n * p), n, p)
colnames(X) <- paste0("x", 1:p)
beta_true <- c(2, -1, 0.5)
y <- as.vector(cbind(1, X) %*% c(1, beta_true) + rnorm(n))

fit <- my_lm(X, y, B = 50)
print(fit)
summary(fit)
```

---

## Plotting Marginals

```{r, eval = FALSE}
plot_marginals(fit)
```

Each panel shows the scatter of `y` versus a predictor `x_j` along with the *marginal fitted line* that holds other variables at their sample means.

---

## License

MIT © 2025 Roberto Molinari

---

## Acknowledgments

Developed for instructional use in statistical computing and regression analysis courses at **Auburn University**.
